Project Notes - Installability

### 2021-06-25 StateOfPractice/Peter-Notes/DomainExptMeeting/Presentation for the Introductory Meeting.tex
Addition of slides comparing the domain expert and SOP lists
Complete draft of slides for Zahra meeting

\bi
\item How does our list compare to the domain expert's list?
\item Is any software missing?
\item Is there software that should be included?
\item Any other questions/comments or concerns?  
\ei

@@

\begin{frame}
\frametitle{Software List}

@@

\begin{frame}
\frametitle{Domain Expert Software List}

@@

\bi
\item So users can pick the right software for their task
\item Think of the software as a family of related software products, like:
\bi
\item Family of automobiles
\item Computer hardware
\item ...
\ei
\item Commonalities
\item Variabilities
\item Parameters of variation
\item Do the following slides capture the commonalities and variabilities?
\item We can follow up over e-mail, if that is easier
\ei

@@

\begin{frame}
\frametitle{Variabilities}

\bi
\item May use parallel processing (May use varied tools for this - MPI, CUDA..)
\item Different equilibrium distribution functions (compressible and incompressible)
\item Coefficients for equilibrium distribution function (based on velocity directions - 2,3,5,9,13,15,19,27)
\item Lattice dimensions (1D, 2D, 3D)
\item Varied velocity directions, partially based on dimensions (2,3,5,9,13,15,19,27)
\item Collision operators (SRT, TRT, MRT, BGK)
\item Collision vs collision-free transport equations
\item Number of fluids that can be modeled simultaneously
\item Fluid parameters (Reynolds Num., density, viscosity, etc.)
\item Lattice boundary (reflective or non-reflective)
\ei

@@

\bi
\item Empirical measures
  \bi
  \item Examples
  \ei
\item Measurement template
  \bi
  \item qualities
  \ei
\item Interview questions
  \bi
  \item Examples
  \ei
  \item AHP Process with pairwise comparisons
\ei
\end{frame}

@@

[Peter and Ao, give the overall ranking graphic for your domain]

@@

\bi
\item We would like feedback on the ranking for each of the qualities
\item Is it feasible to review all 10 graphs, and the associated write-up?
\item Maybe there is a grad student that can review the rankings?
 \ei

@@

\begin{frame}
\frametitle{Discuss Recommendations}

\bi
\item 
\ei

@@

\bi
\item Where should we publish this paper?
\item Who do you see as the targeted readers?
\ei

\begin{frame}
\frametitle{Developer Questions (for next time)}

\bi
\item 
\ei

>>>>

\bi
\item \structure{How does our list compare to the domain expert's list?}
\item \structure{Is any software missing?}
\item \structure{Is there software that should be included?}
\item \structure{Any other questions/comments or concerns?}
\ei

@@

\begin{frame}
\frametitle{SOP Software List}

@@

\begin{frame}
\frametitle{Common With Domain Expert List}

\begin{multicols}{2}	
  \bi
\item \href{https://palabos.unige.ch/}{Palabos}
\item \href{https://www.openlb.net/}{OpenLB}
\item \href{https://github.com/aharwood2/LUMA/}{LUMA}
\item \href{https://www.walberla.net}{waLBerla}
\item \href{http://sailfish.us.edu.pl/}{Sailfish}
\item \href{https://github.com/UCL/hemelb}{HemeLB}
\item \href{http://ccs.chem.ucl.ac.uk/lb3d}{LB3D} - \href{https://www.sciencedirect.com/science/article/pii/S0010465517301017}{paper}
\item \href{https://github.com/carlosrosales/mplabs}{MP-LABS}
\item \href{http://sunlightlb.sourceforge.net/}{SunlightLB}
\item \href{https://pypi.org/project/pylbm/}{pyLBM}
\item  \href{https://www.scd.stfc.ac.uk/Pages/DL_MESO.aspx}{DL\_MESO (LBE)}
\item \href{https://code.google.com/archive/p/limbes/}{LIMBES}
\item \href{https://docs.tclb.io/}{TCLB} (also called CudneLB)
\ei
\end{multicols}

\begin{frame}
\frametitle{Only on Domain Expert List}

%\begin{multicols}{2}	
  \bi
\item ASL (general purpose tool for PDEs, LBM a small part)
\item ch4-project (no docs, no installation guide)
\item Open FSI (uses Palabos for LBM, new project)
\item LIFE (small and new project)
\item LBSIM (dead project)
\item Taxila LBM (dead project, could not install, broken links in
  documentation)                    
	\ei
%\end{multicols}

\begin{frame}
\frametitle{Only on SOP List}

\begin{multicols}{2}	
  \bi
			\item \href{https://ludwig.epcc.ed.ac.uk/}{Ludwig}
			\item \href{http://espressomd.org/wordpress/}{ESPResSo}

			\item \href{https://github.com/maxlevesque/laboetie}{laboetie}
			\item \href{http://mechsys.nongnu.org/}{MechSys}
			\item \href{https://github.com/Olllom/lettuce}{lettuce}
			\item \href{https://github.com/espressopp/espressopp}{ESPResSo++}

			\item \href{http://faculty.fiu.edu/~sukopm/LBnD_Prime/LBnD_Prime.html}{LB2D-Prime}

			\item \href{https://pypi.org/project/lbmpy/}{lbmpy}	
			\item \href{http://faculty.fiu.edu/~sukopm/LBnD_Prime/LBnD_Prime.html}{LB3D-Prime}	
			\item \href{https://github.com/UCL/LatBo.jl}{LatBo.jl}
	\ei
\end{multicols}

\structure{Why is pylbm on the domain expert list twice, should one be lbmpy?}

@@

\bi
\item So users can pick the right software for their task
\item Think of the software as a family of related software products, like:
\bi
\item Family of automobiles
\item Computer hardware
\item etc.
\ei
\item Commonalities
\item Variabilities
\item Parameters of variation
\item \structure{Do the following slides capture the commonalities and variabilities?}
\item We can follow up over e-mail, if that is easier
\ei

@@

\begin{frame}
\frametitle{SOP Variabilities}

\bi
\item May use parallel processing (May use varied tools for this - MPI, CUDA..)
\item Different equilibrium distribution functions (compressible and incompressible)
\item Coefficients for equilibrium distribution function (based on velocity
  directions - 2, 3, 5, 9, 13, 15, 19, 27)
\item Lattice dimensions (1D, 2D, 3D)
\item Varied velocity directions, partially based on dimensions (2, 3, 5, 9, 13,
  15, 19, 27)
\item Collision operators (SRT, TRT, MRT, BGK)
\item Collision vs collision-free transport equations
\item Number of fluids that can be modeled simultaneously
\item Fluid parameters (Reynolds num., density, viscosity, etc.)
\item Lattice boundary (reflective or non-reflective)
\ei

\begin{frame}
\frametitle{Domain Expert Variabilities}

\bi
\item May use parallel processing (MPI, CUDA, OpenMP, ...)
\item Lattice dimensions (1D, 2D, 3D)
\item Turbulent (Yes, No)
\item FSI (Fluid Structure Interaction)
\item Complex Geometry
\item Non-Newtonian Fluids
\item Programming Language (C++, Python, etc)
\ei

@@

\bi
\item Empirical measures (number of stars, forks, pull requests, lines of code, etc)
\item Measurement template
  \bi
\item Installability
\item Correctness and verifiability
\item Surface reliability
\item Surface robustness
\item Surface usability
\item Maintainability
\item Surface Understandability
  \item Visibility and transparency
  \ei
\item Developer interviews (looking for pain points)
\item AHP Process with pairwise comparisons
  \ei
\end{frame}

@@

\bigskip

    \includegraphics[width=1.0\textwidth]{finalscore_chart.png}

@@

\bi
\item \structure{We would like feedback on the ranking for each of the qualities}
\item \structure{Is it feasible to review all 10 graphs, and the associated write-up?}
\item \structure{Maybe there is a grad student that can review the rankings?}
\ei

@@

\begin{frame}
\frametitle{Pain Points from Developer Interviews}

\structure{Do these fit with your experience?}
\bi
\item Lack of time to implement new features
\item Team members lack software development experience
\item Lack of funding for software development
\item No organizations to help with developing high quality software
\item Documentation could be improved, only has shallow overview of the theory
\item Setting up parallelization is challenging
\item Setting up continuous integration is challenging
\item Difficulties in ensuring correctness because of size of test cases
\item Users sometimes use tools inappropriately
\item Technical debt due to coupling between components
  \ei

\begin{frame}
\frametitle{Recommendations}

\structure{Do these seem feasible?  What other ideas do we have?}
\bi
\item Consult with software development organization
  \bi
\item Better Scientific Software (BSSw)
\item Software Sustainability Institute
\item Software Carpentry
  \ei
\item Citations for software (Katz project)
  \item Redefine productivity to include time working on tasks like testing, continuous
    integration and documentation
\ei

@@

\bi
\item \structure{Who do you see as the targeted readers?}
\item \structure{Where should we publish this paper?}
\ei
